% Copyright (c) Patrick Haas. All rights reserved.
%
% Licensed under the BSD license. See LICENSE.txt
% in the project root for license information.

% s. https://typefacts.com/artikel/kerningtest
I “Ask Jeff” or ‘Ask Jeff’. Take the chef d’œuvre! \emph{Two of [of] (of) 
‘of’ “of” of? of! of*.}\emph{Two of [of] (of) ‘of’ “of” of? of! of*}. Ydes,
Yffignac and Ygrande are in France: so are Ypres, Les Woëvres, the Fôret
de Wœvres, the Voire and Vauvise. Yves is in heaven; D’Amboise is in jail.
Lyford’s in Texas \& L’Anse-aux-Griffons in Québec; the Łyna in Poland.
Yriarte, Yciar and Ysaÿe are at Yale. Kyoto and Ryotsu are both in Japan,
Kwikpak on the Yukon delta, Kvæven in Norway, Kyulu in Kenya, not in
Rwanda.…Walton’s in West Virginia, but «Wren» is in Oregon. Tlálpan is
near Xochimilco in México. The Zygos \& Xylophagou are in Cyprus, Zwettl
in Austria, Fænø in Denmark, the Vøringsfossen and Værøy in Norway. Tchula
is in Mississippi, the Tittabawassee in Michigan. Twodot is here in Montana,
Ywamun in Burma. Yggdrasil and Ymir, Yngvi and Vóden, Vídrið and Skeggjöld
and Týr are all in the Eddas. Tørberget and Våg, of course, are in Norway,
Ktipas and Tmolos in Greece, but Vázquez is in Argentina, Vreden in
Germany, Von-Vincke-Straße in Münster, Vdovino in Russia, Ytterbium in the
periodic table. Are Toussaint L’Ouverture, Wölfflin, Wolfe, Miłosz and Wū Wŭ
all in the library? 184-110, 1510--1620, 1620---1730, 11:00 pm, and the 1980s
are over. Em---dashes are larger than en--dashes are longer than 
old-fashioned hyphens.

Ist da „Jemand“? „Volker?“ – „Wolf“. „Anna?“ – „Yvonne“. „Torsten fragte:
‚Vladimir?‘, später rief er ‚Wolf‘ und ‚Theresa‘, dann ‚Andreas‘ und ‚Yvonne‘“.
Eleganter: Ist da »Jemand«? »Volker?« – »Wolf«. »Anna?« – »Yvonne«. »Torsten
fragte: ›Vladimir?‹, später rief er ›Wolf‹ und ›Theresa‹, dann ›Andreas‹ 
und ›Yvonne‹«.

% for embrac
\emph{%
a[a]a b[b]b c[c]c d[d]d e[e]e f[f]f %
g[g]g h[h]h i[i]i j[j]j k[k]k l[l]l %
m[m]m n[n]n o[o]o p[p]p q[q]q r[r]r %
s[s]s t[t]t u[u]u v[v]v w[w]w x[x]x %
y[y]y z[z]z.%
} \par
\emph{%
A[A]A B[B]B C[C]C D[D]D E[E]E F[F]F %
G[G]G H[H]H I[I]I J[J]J K[K]K L[L]L %
M[M]M N[N]N O[O]O P[P]P Q[Q]Q R[R]R %
S[S]S T[T]T U[U]U V[V]V W[W]W X[X]X %
Y[Y]Y Z[Z]Z.%
} \par
{\addfontfeatures{Numbers={Proportional,OldStyle}}%
\emph{%
0[0]0 1[1]1 2[2]2 3[3]3 4[4]4 %
5[5]5 6[6]6 7[7]7 8[8]8 9[9]9
}} \par
{\addfontfeatures{Numbers={Proportional,Lining}}%
\emph{%
0[0]0 1[1]1 2[2]2 3[3]3 4[4]4 %
5[5]5 6[6]6 7[7]7 8[8]8 9[9]9
}} \par
{\addfontfeatures{Numbers={Monospaced,Lining}}%
\emph{%
0[0]0 1[1]1 2[2]2 3[3]3 4[4]4 %
5[5]5 6[6]6 7[7]7 8[8]8 9[9]9
}} \par
\emph{%
[“Ask Jeff”] [‘Ask Jeff’] [„Wolf“] [„Wolf“?] [„Wolf“!] [„Wolf“.] [„Wolf“,] [„Wolf“;]%
[‚Wolf‘]} \par
\emph{%
[›Vladimir?‹] [«Wren»] [mâitre d’] [ä] [ö] [ü] %
[vérité] [/] [\&]
} \par
\emph{%
[Ä] [Ö] [Ü]
}
